Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-04 paper.qmd
Five Gaussian clusters with enough bins..earlier was too much

## Compute hexbin parameters
num_bins_x_gau1 <- 40
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(97)))

>>>>

## Compute hexbin parameters
num_bins_x_gau1 <- 16
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(97)))
